\section{Introduction}

The smart home is an important application domain of the Internet of Things (IoT), where automation rules connect devices, sensors, and environmental events to automate daily tasks. Most automation rules follow the Trigger-Condition-Action (TCA) model. As the number of automation rules grows, unintended rule interaction becomes more likely and may further evolve into rule conflicts, disrupting expected automation and causing security or safety risks.

Consider a simple example. Rule R1 enables the sprinkler when smoke is detected, and Rule R2 closes the water valve when a leak is detected. Each rule is reasonable in isolation, but their interaction may create a rule conflict that disables firefighting: once R1 activates the sprinkler, the resulting water flow may be interpreted as a leak and trigger R2, which closes the valve and cuts off the sprinkler's water supply. This example shows that individually legitimate automation rules may still produce harmful system-level behavior when they interact.

Recent work has further investigated rule conflict detection in IoT-based smart homes \cite{huang2023survey,huang2021conflict,li2020diac,trimananda2020understanding,yagita2015application,chaki2020fine,yu2022tapinspector,pradeep2021automating}. Existing approaches mainly include security-policy-based methods, formal verification methods, and pattern-based methods. Security-policy-based methods check whether rule execution violates predefined security policies \cite{celik2018soteria,celik2019iotguard,ding2021iotsafe,hsu2019safechain}. Formal verification methods verify rule consistency and safety properties through rule models and property checking \cite{sun2014conflict,ibrhim2020formal,yu2022tapinspector}. pattern-based methods identify suspicious interaction structures, such as race condition, chained triggering, and conflicting actions \cite{alhanahnah2022iotcom,chi2020cross,chi2023detecting,li2020diac,xiao2019a3id,trimananda2020understanding,chaki2020fine}. Although these approaches are useful, they still have difficulty determining whether a rule interaction should be treated as a candidate rule conflict in a specific smart home setting.

This challenge arises from three factors. First, rule conflict is context-dependent. Because smart homes are heterogeneous and user preferences differ, the same rule interaction may be benign in one deployment but unsafe in another, leading to false positives or false negatives under generic detection logic. Second, many rule interactions propagate through physical channels such as temperature, humidity, and light. If a system uses environmental abstractions and ignores zone characteristics such as thermal isolation, it may misidentify interaction edges \cite{celik2019iotguard,alhanahnah2022iotcom,chen2019multi,wang2019charting}. Third, runtime confirmation of candidate rule conflicts remains difficult. Although static analysis is comprehensive, it often over-approximates without the current system state. Existing dynamic or hybrid systems can monitor rule events and physical contexts \cite{ding2021iotsafe}, yet they do not explicitly verify whether a candidate conflict edge is actually activated at rule-trigger time.

To address these limitations, we build on three observations. Rule interaction exists not only at the logical layer but also propagates through physical channels in different zones, which requires a rule model that captures both spatial and environmental effects. Rule interaction and rule conflict should be explicitly distinguished, and the user-defined Entity Safety Configuration is used to determine whether a rule interaction should be retained as a candidate rule conflict. Finally, combining candidate conflict edges derived from static analysis with the current system state through assertion verification can reduce the over-approximation introduced by static analysis alone. Based on these observations, we propose a hybrid framework that combines offline static analysis with runtime dynamic monitoring. In the static phase, we apply formal verification to construct the Rule Interaction Dependency Graph (RIDG) and then extract the Rule Conflict Dependency Graph (RCDG) according to the user-defined Entity Safety Configuration. In the runtime phase, we use assertion verification to check whether candidate conflict edges in the RCDG are activated under the current system state, thereby identifying impending rule conflicts at runtime.

In summary, our main contributions are as follows:

\begin{itemize}
	\item We extend automation rule modeling to the Trigger-Condition-Action-Environment (TCAE) model and use the Rule Interaction Dependency Graph (RIDG), the Rule Conflict Dependency Graph (RCDG), and the Entity Safety Configuration to distinguish general rule interaction from candidate rule conflicts.

	\item We design and implement a hybrid detection framework in which static analysis pre-screens interactions and limits runtime checking to candidate conflict edges instead of the full rule set.

	\item We implement a runtime mechanism based on assertion verification that combines the current system state with temporal evidence to determine whether a candidate conflict edge is activated and to report impending rule conflicts.
\end{itemize}