\section{Related Work}

\begin{table*}[htbp]
	\centering
	\caption{Comparison of IoT Rule Conflict Detection Approaches}
	\label{Relate_Work}
	\begin{adjustbox}{width=0.98\textwidth}
		\begin{tabular}{|l|c|c|c|l|c|c|c|l|}
			\hline
			\textbf{Name} & \textbf{DIC} & \textbf{Physical Channel} & \textbf{Zone Awareness} & \textbf{Detection Method} & \textbf{Runtime Verification} & \textbf{User Preference} & \textbf{User Effort} & \textbf{Generalization} \\
			\hline
			\textbf{Soteria\cite{celik2018soteria}} & T & F & F & Static & F & F & High & Low \\
			\hline
			\textbf{IoTGuard\cite{celik2019iotguard}} & T & F & F & Dynamic & F & F & Med & Low \\
			\hline
			\textbf{SafeChain\cite{hsu2019safechain}} & T & F & F & Static & F & F & Med & Med \\
			\hline
			\textbf{iRuler\cite{wang2019charting}} & T & T* & T* & Static & F & F & Low & Low \\
			\hline
			\textbf{IoTIE\cite{chen2019multi}} & T & T & T* & Static & F & F & Low & Med \\
			\hline
			\textbf{IoTSafe\cite{ding2021iotsafe}} & T & T & T & Hybrid & F & F & Very High & High \\
			\hline
			\textbf{IoTCom\cite{alhanahnah2022iotcom}} & F & T & F & Static & F & F & High & Med \\
			\hline
			\textbf{IoTMediator\cite{chi2023detecting}} & F & F & F & Hybrid & F & T & High & High \\
			\hline
			\textbf{Ours} & \textbf{T} & \textbf{T} & \textbf{T} & \textbf{Hybrid} & \textbf{T} & \textbf{T} & \textbf{Low} & \textbf{High} \\
			\hline
		\end{tabular}
	\end{adjustbox}
	\par\vspace{4pt}
	\footnotesize
	\noindent\textbf{Note:} "DIC" means distinguishing rule interaction from candidate rule conflicts. "Runtime Verification" means checking whether a candidate conflict edge is activated when a rule is triggered. "T*" indicates partial support or support that depends on deployment-specific input.
\end{table*}

Prior work on rule conflict detection for smart home systems spans security-policy checking, formal verification, interaction-pattern analysis, and hybrid detection. Huang et al.~\cite{huang2023survey} note that the problem definition, detection target, and conflict taxonomy of smart-home rule conflict detection are still not fully unified. Table~\ref{Relate_Work} compares representative approaches.

Security-policy-based and formal-verification approaches detect conflicts by checking predefined policies, attributes, or formal safety properties. Soteria~\cite{celik2018soteria}, IoTGuard~\cite{celik2019iotguard}, SafeChain~\cite{hsu2019safechain}, IoTSan~\cite{nguyen2018iotsan}, and IoTSafe~\cite{ding2021iotsafe} rely on predefined policies, templates, or formal properties to identify unsafe behaviors. Formal-verification approaches, such as those of Sun et al.~\cite{sun2014conflict}, Ibrhim et al.~\cite{ibrhim2020formal}, and TapInspector~\cite{yu2022tapinspector}, verify rule consistency and safety properties over formal rule models. These approaches are effective for known policies or properties, but their coverage depends on the availability of suitable rules.

Interaction-pattern-based approaches identify suspicious relations among automation rules rather than directly checking policy violations. IoTCom~\cite{alhanahnah2022iotcom} detects potential interactions, including physical-channel-related ones, through static analysis. HomeGuard~\cite{trimananda2020understanding} and IoTMediator~\cite{chi2023detecting} enumerate representative interaction threats from empirical observations. While these methods can reveal many logical associations, they do not always distinguish benign interaction from candidate rule conflicts, especially when the interaction is part of an intended feedback loop.

Compared with these approaches, our framework combines physical-channel-aware rule modeling, zone-aware analysis, user-defined Entity Safety Configuration, and runtime assertion verification. It distinguishes general rule interaction from candidate rule conflicts and checks whether the corresponding candidate conflict edge is activated at runtime.