\section{Introduction}

The rapid growth of the Internet of Things has made smart home automation increasingly common. Users manage these environments through Trigger-Action Programming (TAP) rules, which define how devices respond to specific events or conditions. While these rules provide convenience, they often create complex dependencies. Rules can interact not only through direct device states but also through the shared physical environment. For example, enabling a sprinkler upon smoke detection may indirectly trigger a leak-response rule that closes the water valve, undermining firefighting~\cite{chi2023detecting}. These interactions can lead to rule conflicts that compromise the safety and comfort of the inhabitants~\cite{huang2023survey,trimananda2020understanding,chi2023detecting}.

% The smart home is an important application domain of the Internet of Things (IoT), where automation rules connect devices, sensors, and environmental events to automate daily tasks. Most automation rules follow the Trigger-Condition-Action (TCA) model. As the number of automation rules grows, unintended rule interaction becomes more likely and may further evolve into rule conflicts, disrupting expected automation and causing security or safety risks \cite{huang2023survey,trimananda2020understanding,chi2023detecting}. For example, enabling a sprinkler upon smoke detection may indirectly trigger a leak-response rule that closes the water valve, undermining firefighting \cite{chi2023detecting}.

Identifying these conflicts remains a significant challenge~\cite{huang2023survey,huang2021conflict,li2020diac,trimananda2020understanding,yagita2015application,chaki2020fine,yu2022tapinspector,pradeep2021automating}. Existing research primarily focuses on static analysis to detect logical overlaps between rules. 
% Security-policy-based methods~\cite{celik2018soteria,celik2019iotguard,ding2021iotsafe,hsu2019safechain,sun2014confict,ibrhim2020formal} check whether rule execution violates predefined safety or security policies, often by modeling automation rules and checking safety properties over the resulting models. Pattern-based methods~\cite{alhanahnah2022iotcom,chi2020cross,chi2023detecting,li2020diac,xiao2019a3id,trimananda2020understanding,chaki2020fine} identify suspicious interaction structures, such as race condition, chained triggering, and conflicting actions. 
These methods often treat all physical interactions as potential conflicts, regardless of the spatial context, leading to a high number of false positives. Physical effects like heat or light propagation are often confined to specific zones. A rule governing a heater in the bedroom rarely interferes with a cooler in a distant greenhouse. Approaches that ignore zone boundaries may infer non-existent interactions~\cite{celik2019iotguard,alhanahnah2022iotcom,chen2019multi,wang2019charting}. Furthermore, the definition of a conflict is highly dependent on the specific application scenario and user intent. An automation that opens a window when the temperature rises might be a security risk in a bedroom. The same behavior is often the desired outcome in a greenhouse to protect plants. Current tools lack the flexibility to incorporate these contextual nuances and user preferences. Static analysis also tends to over-approximate system behavior, flagging interactions that may never occur during actual execution.

% Recent work has further investigated rule conflict detection in IoT-based smart homes \cite{huang2023survey,huang2021conflict,li2020diac,trimananda2020understanding,yagita2015application,chaki2020fine,yu2022tapinspector,pradeep2021automating}. Existing approaches mainly include security-policy-based methods and pattern-based methods. Security-policy-based methods check whether rule execution violates predefined safety or security policies, often by modeling automation rules and checking safety properties over the resulting models \cite{celik2018soteria,celik2019iotguard,ding2021iotsafe,hsu2019safechain,sun2014conflict,ibrhim2020formal}. Pattern-based methods identify suspicious interaction structures, such as race condition, chained triggering, and conflicting actions \cite{alhanahnah2022iotcom,chi2020cross,chi2023detecting,li2020diac,xiao2019a3id,trimananda2020understanding,chaki2020fine}. Although these approaches are useful, they still have difficulty determining whether a rule interaction should be treated as a candidate rule conflict in a specific smart home setting.

% This challenge arises from three factors. First, rule conflict is context-dependent. Because smart homes are heterogeneous and user preferences differ, the same rule interaction may be benign in one deployment but unsafe in another, leading to false positives or false negatives under generic detection logic. Second, many interactions propagate through physical channels with zone-dependent propagation (e.g., thermal isolation), so detectors that ignore zone boundaries may infer non-existent interactions \cite{celik2019iotguard,alhanahnah2022iotcom,chen2019multi,wang2019charting}. Third, runtime confirmation of candidate rule conflicts remains difficult. Although static analysis is comprehensive, it often over-approximates without the current system state. Existing dynamic or hybrid systems can monitor rule events and physical contexts \cite{ding2021iotsafe}, yet they do not explicitly verify whether a candidate conflict edge is actually activated at rule-trigger time.

To address these limitations, our key insight is that \textbf{the validity of a conflict report depends on the intersection of physical reachability and user-defined safety boundaries.} We observe that a rule interaction only becomes a genuine conflict if the physical influence can traverse spatial boundaries and violate the specific security requirements of a given zone. This suggests that a detection system should not treat all logical dependencies equally. Instead, it must first filter potential interactions based on their environmental constraints and user intent before attempting to verify them. We also recognize that the inherent uncertainty of static analysis can only be resolved by observing the actual system state at the moment of rule execution.

In this paper, we propose a hybrid detection framework that integrates static environment-aware modeling with runtime validation. We first extend the standard TAP paradigm into a Trigger-Condition-Action-Environment (TCAE) model to capture how actions affect physical channels within specific zones. This model enables the construction of a Rule Interaction Dependency Graph (RIDG) that respects spatial isolation. To account for varying user needs, the framework utilizes an entity safety configuration to prune benign interactions, producing a refined Rule Conflict Dependency Graph (RCDG). Finally, a runtime monitoring component performs assertion verification. By checking real-time device states and timing constraints, the system confirms whether a candidate conflict from the RCDG is actually triggered during system operation.

% To address these limitations, we draw three insights. Rule interaction exists not only at the logical layer but also propagates through physical channels in different zones, which requires a rule model that captures both spatial and environmental effects. Rule interaction and rule conflict should be explicitly distinguished, and the user-defined Entity Safety Configuration is used to determine whether a rule interaction should be retained as a candidate rule conflict. Finally, combining candidate conflict edges derived from static analysis with the current system state through assertion verification can reduce the over-approximation introduced by static analysis alone. Based on these observations, we propose a hybrid framework that combines offline static analysis with runtime dynamic monitoring. In the static phase, we apply formal verification to construct the Rule Interaction Dependency Graph (RIDG) and then extract the Rule Conflict Dependency Graph (RCDG) according to the user-defined Entity Safety Configuration. In the runtime phase, we use assertion verification to check whether candidate conflict edges in the RCDG are activated under the current system state, thereby identifying impending rule conflicts at runtime.

In summary, our main contributions are as follows:

\begin{itemize}
	\item We propose the TCAE model to characterize implicit rule interactions through zone-dependent physical channel propagation. This modeling approach enables the system to accurately identify potential conflicts that are often incorrectly flagged by methods lacking environmental awareness.
	
	\item We design a hybrid detection framework is developed to integrate static graph analysis with runtime assertion verification. The framework leverages an entity safety configuration to prune benign interactions based on user-defined security boundaries, ensuring high precision while maintaining detection coverage.
	
	\item We implement the system on the Home Assistant platform and evaluate it in a multi-zone testbed. The results demonstrate that our approach effectively eliminates nine false positives reported by the state-of-the-art tool IoTMediator and maintains millisecond-level computational overhead.

	% \item We extend automation rule modeling to the Trigger-Condition-Action-Environment (TCAE) model and use the RIDG, the RCDG, and the Entity Safety Configuration to distinguish general rule interaction from candidate rule conflicts.

	% \item We design a hybrid detection framework in which static analysis pre-screens interactions and limits runtime checking to candidate conflict edges instead of the full rule set.

	% \item We implement a runtime mechanism based on assertion verification that combines the current system state with temporal evidence to determine whether a candidate conflict edge is activated; in our testbed, it eliminates nine false positives reported by IoTMediator while keeping runtime overhead at the millisecond level.
\end{itemize}